### 2025-05-25 sports-cognitive-psychology.qmd
20250524 - clean up

$$
\begin{aligned}
  \text{expected value} &= \text{Sum}(\text{Probabilities} \times \text{Payouts}) \\
  \text{expected value} &= (\text{Reversal \%})(\text{Positive change in Winning Probability of a Reversal}) + (1 - \text{Reversal \%})(\text{Negative change in Winning Probability of Losing a Timeout})
\end{aligned}
$$ {#eq-challengingCall}

>>>>

$$
\begin{aligned}
  \text{expected value} &= \text{Sum}(\text{Probabilities} \times \text{Payouts}) \\
  &= (\text{Reversal \%})(\text{Positive change in Winning Probability of a Reversal}) \\
  &\quad + (1 - \text{Reversal \%})(\text{Negative change in Winning Probability of Losing a Timeout})
\end{aligned}
$$ {#eq-challengingCall}
